---
title: "TCGA-TCEM"
author: "Balazs Koncz"
date: '2020 10 20 '
output: html_document
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.path = "Figs/"
)
setwd("d:/CloudStation/mygit/fitness-modell-bk/")
ext_folder1 = "d:/CloudStation/fitness-model-ext/"
library(dplyr)
library(magrittr)
library(tibble)
library(fastmatch)
library(ggplot2)
library(forcats)
library(stringi)
library(Rfast)
library(tidyr)
library(parallel)
library(survival)
library(survminer)
'%nin%' = Negate('%in%')
fillnafun = function(v,l) {
  outvec = c(v,rep(NA,l-length(v)))
  names(outvec) = NULL
  outvec
}
```

#Driver or passenger mutations

```{r}
ids = list.files(paste0(ext_folder1, "recogn_matrices_neo")) #8943
study_abbrev = read.delim(paste0(ext_folder1, "study_abbrev.txt"), stringsAsFactors = F)
study_abbrev$abb = tolower(study_abbrev$abb)
save(study_abbrev, file = paste0(ext_folder1,"objects/study_abbrev"))

mutfreq = lapply(ids, function(x) {
  #NEO
  load(paste0(ext_folder1, "neoeps/", x))
  names(neoeps_list)
})
mutfreq = do.call(c,mutfreq)
temp = table(mutfreq)
mutfreq = as.numeric(temp)
names(mutfreq) = names(temp)
rm(temp)
driver = names(mutfreq)[mutfreq>1]
#passenger = names(mutfreq)[mutfreq==1]
save(driver, file = paste0(ext_folder1, "objects/driver_mutations"))
rm(mutfreq)

# tt = sapply(ids, function(x) {
#   load(paste0(ext_folder1, "ttypes/", x))
#   ttype
# })
# save(tt, file = paste0(ext_folder1,"objects/tumortypes"))
# tumors = sort(unique(tt))
# save(tumors, file = paste0(ext_folder1,"objects/tumors"))

```


```{r}
# load(paste0(ext_folder1, "recogn_matrices_orig/TCGA-02-0003-01")) #recogn_matrices
# load(paste0(ext_folder1, "recogn_matrices_neo/TCGA-02-0003-01")) #recogn_matrices
# load(paste0(ext_folder1, "origeps/TCGA-02-0003-01")) #origeps_list
# load(paste0(ext_folder1, "neoeps/TCGA-02-0003-01")) #neoeps_list
# load(paste0(ext_folder1, "ttypes/TCGA-02-0003-01")) #ttype

ids = list.files(paste0(ext_folder1, "recogn_matrices_neo")) #8943
nonamer_selection = function(p,n) {
  if(n == 0 | p<4) {
    c(F,F,F,F,F,F,F,F,F)
  } else if(n == 2) {
    c(F,T,F,F,F,F,F,F,F)
  } else if(n == 3) {
    c(F,T,T,F,F,F,F,F,F)
  } else if(n == 4 & p == 4) {
    c(T,F,F,F,F,F,F,F,F)
  } else if(n == 4 & p != 4) {
    c(F,T,T,T,F,F,F,F,F)
  } else if(n == 4 & p == 5) {
    c(T,T,F,F,F,F,F,F,F)
  } else if(n == 5 & p != 5) {
    c(F,T,T,T,T,F,F,F,F)
  } else if(n == 6 & p == 6) {
    c(T,T,T,F,F,F,F,F,F)
  } else if(n == 6 & p != 6) {
    c(F,T,T,T,T,T,F,F,F)
  } else if(n == 7 & p == 7) {
    c(T,T,T,T,F,F,F,F,F)
  } else if(n == 7 & p != 7) {
    c(F,T,T,T,T,T,F,F,F)
  } else if(n == 8 & p == 8) {
    c(T,T,T,T,T,F,F,F,F)
  } else if(n == 8 & p != 8) {
    c(F,T,T,T,T,T,F,F,F)
  } else {
    c(F,T,T,T,T,T,F,F,F)
  }
}

lapply(ids, function(x) {
  #NEO
  load(paste0(ext_folder1, "neoeps/", x))
  load(paste0(ext_folder1, "recogn_matrices_neo/", x))
  neoeps_list = lapply(neoeps_list, function(y) y[nchar(y) == 9])
  pos = as.numeric(gsub("[[:upper:]]","",sapply(strsplit(names(neoeps_list),"\\."), function(z) z[3]))) #mutation positions
  n9mers = lengths(neoeps_list) #hany nonamer tartozik egy mutaciohoz
  tmn = lapply(1:length(neoeps_list), function(u) neoeps_list[[u]][nonamer_selection(pos[u],n9mers[u])]) #nonamers which carry mutation in TCEM position
  names(tmn) = names(neoeps_list)
  tmn_unlist = unlist(tmn)
  names(tmn_unlist) = sapply(names(tmn_unlist), function(v) substr(v,1,(nchar(v)-1)))
  tmn_unlist = tmn_unlist[!is.na(tmn_unlist)]
  #STRONG NEO
  aff_str_tmn_indices = colMins(recogn_matrices$aff[,tmn_unlist], value = T)<50
  aff_str_tmn = tmn_unlist[aff_str_tmn_indices] #ezeket kell venni az origbol is!!
  rp_str_tmn_indices = colMins(recogn_matrices$rp[,tmn_unlist], value = T)<0.5
  rp_str_tmn = tmn_unlist[rp_str_tmn_indices] #ezeket kell venni az origbol is!!
  #WEAK NEO
  aff_weak_tmn_indices = colMins(recogn_matrices$aff[,tmn_unlist], value = T)<500
  aff_weak_tmn = tmn_unlist[aff_weak_tmn_indices] #ezeket kell venni az origbol is!!
  rp_weak_tmn_indices = colMins(recogn_matrices$rp[,tmn_unlist], value = T)<2
  rp_weak_tmn = tmn_unlist[rp_weak_tmn_indices] #ezeket kell venni az origbol is!!
  #ORIG
  load(paste0(ext_folder1, "origeps/", x))
  load(paste0(ext_folder1, "recogn_matrices_orig/", x))
  origeps_list = lapply(origeps_list, function(y) y[nchar(y) == 9])
  tmo = lapply(1:length(origeps_list), function(u) origeps_list[[u]][nonamer_selection(pos[u],n9mers[u])])
  names(tmo) = names(origeps_list)
  tmo_unlist = unlist(tmo)
  names(tmo_unlist) = sapply(names(tmo_unlist), function(v) substr(v,1,(nchar(v)-1)))
  tmo_unlist = tmo_unlist[!is.na(tmo_unlist)]
  #STRONG ORIG
  aff_str_tmo = tmo_unlist[aff_str_tmn_indices] #ezeket vettuk a neobol!!
  rp_str_tmo = tmo_unlist[rp_str_tmn_indices] #ezeket vettuk a neobol!!
  #WEAK ORIG
  aff_weak_tmo = tmo_unlist[aff_weak_tmn_indices]
  rp_weak_tmo = tmo_unlist[rp_weak_tmn_indices]

  or_str_tmn = unique(cbind(c(aff_str_tmn, rp_str_tmn),c(aff_str_tmo, rp_str_tmo)))[,1]
  or_str_tmo = unique(cbind(c(aff_str_tmn, rp_str_tmn),c(aff_str_tmo, rp_str_tmo)))[,2]
  or_weak_tmn = unique(cbind(c(aff_weak_tmn, rp_weak_tmn),c(aff_weak_tmo, rp_weak_tmo)))[,1]
  or_weak_tmo = unique(cbind(c(aff_weak_tmn, rp_weak_tmn),c(aff_weak_tmo, rp_weak_tmo)))[,2]
  
  temp_str = cbind(c(aff_str_tmn, rp_str_tmn),c(aff_str_tmo, rp_str_tmo))[duplicated(cbind(c(aff_str_tmn, rp_str_tmn),c(aff_str_tmo, rp_str_tmo))),,drop=F]
  and_str_tmn = temp_str[,1]
  and_str_tmo = temp_str[,2]
  temp_weak = cbind(c(aff_weak_tmn, rp_weak_tmn),c(aff_weak_tmo, rp_weak_tmo))[duplicated(cbind(c(aff_weak_tmn, rp_weak_tmn),c(aff_weak_tmo, rp_weak_tmo))),,drop=F]
  and_weak_tmn = temp_weak[,1]
  and_weak_tmo = temp_weak[,2]
  
  #JOIN INTO A LIST
  tmn_list = list(tmn = tmn,tmn_unlist = tmn_unlist,aff_str_tmn = aff_str_tmn,rp_str_tmn = rp_str_tmn,or_str_tmn = or_str_tmn,and_str_tmn = and_str_tmn,aff_weak_tmn = aff_weak_tmn,rp_weak_tmn = rp_weak_tmn,or_weak_tmn = or_weak_tmn,and_weak_tmn = and_weak_tmn, tmo = tmo,tmo_unlist = tmo_unlist,aff_str_tmo = aff_str_tmo,rp_str_tmo = rp_str_tmo,or_str_tmo = or_str_tmo,and_str_tmo = and_str_tmo,aff_weak_tmo = aff_weak_tmo,rp_weak_tmo = rp_weak_tmo,or_weak_tmo = or_weak_tmo,and_weak_tmo = and_weak_tmo)
  save(tmn_list, file = paste0(ext_folder1,"tcem_mutated_nonamers/", x))
})

# mutonlydf[mutonlydf$nnonamers == 1|mutonlydf$nnonamers == 5|mutonlydf$position < 4,5:13] = c(F,F,F,F,F,F,F,F,F) #Excluded: nnonamers == 1 - aa data is unknown; position = 1,2 or 3 - mutation is not in TCEM (at the begining of the protein); nonamers = 5 - mutation is not in TCEM (at the end of the protein)
# mutonlydf[mutonlydf$nnonamers == 10,5:13] = c(F,T,F,F,F,F,F,F,F) #last-1 position - 2 nonamer: 2. kell
# mutonlydf[mutonlydf$nnonamers == 15,5:13] = c(F,T,T,F,F,F,F,F,F) #last-2 position - 3 nonamer: 2. es 3. kell
# mutonlydf[mutonlydf$nnonamers == 20 & mutonlydf$position == 4,5:13] = c(T,F,F,F,F,F,F,F,F) #4 nonamer: 1. kell (4. pozicioban van a mut)
# mutonlydf[mutonlydf$nnonamers == 20 & mutonlydf$position != 4,5:13] = c(F,T,T,T,F,F,F,F,F) #last-3 position: 4 nonamer: 2-4. kell (8,7,6 poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 25 & mutonlydf$position == 5,5:13] = c(T,T,F,F,F,F,F,F,F) #5 nonamer: 1-2. kell (5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 25 & mutonlydf$position != 5,5:13] = c(F,T,T,T,T,F,F,F,F) #last-4 position: 5 nonamer: 2-5. kell (8,7,6,5. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 30 & mutonlydf$position == 6,5:13] = c(T,T,T,F,F,F,F,F,F) #6 nonamer: 1-3. kell (6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 30 & mutonlydf$position != 6,5:13] = c(F,T,T,T,T,T,F,F,F) #last-5 position: 6 nonamer: 2-6. kell (8,7,6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 35 & mutonlydf$position == 7,5:13] = c(T,T,T,T,F,F,F,F,F) #7 nonamer: 1-4. kell (7,6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 35 & mutonlydf$position != 7,5:13] = c(F,T,T,T,T,T,F,F,F) #last-6 position: 7 nonamer: 2-6. kell (8,7,6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 40 & mutonlydf$position == 8,5:13] = c(T,T,T,T,T,F,F,F,F) #8 nonamer: 1-5. kell (8,7,6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers == 40 & mutonlydf$position != 8,5:13] = c(F,T,T,T,T,T,F,F,F) #last-7 position: 8 nonamer: 2-6. kell (8,7,6,5,4. poziciokban van a mut)
# mutonlydf[mutonlydf$nnonamers > 40 & mutonlydf$position > 8,5:13] = matrix(c(F,T,T,T,T,T,F,F,F), byrow = T) #others

load("D:/CloudStation/fitness-model-ext/tcem_mutated_nonamers/TCGA-04-1346-01")
```

#Original and neo TCEM frequencies
##Calculation

```{r}
ids = list.files(paste0(ext_folder1, "tcem_mutated_nonamers/")) #8943
load(paste0(ext_folder1, "objects/pentamerfreq_tcem"))

lapply(ids, function(x) {
  load(paste0(ext_folder1, "tcem_mutated_nonamers/", x))
  aff_str_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$aff_str_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(aff_str_orig)>0) names(aff_str_orig) = paste0(names(tmn_list$aff_str_tmo),".",substr(tmn_list$aff_str_tmo,4,8))
  rp_str_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$rp_str_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(rp_str_orig)>0) names(rp_str_orig) = paste0(names(tmn_list$rp_str_tmo),".",substr(tmn_list$rp_str_tmo,4,8))
  and_str_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$and_str_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(and_str_orig)>0) names(and_str_orig) = paste0(names(tmn_list$and_str_tmo),".",substr(tmn_list$and_str_tmo,4,8))
  or_str_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$or_str_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(or_str_orig)>0) names(or_str_orig) = paste0(names(tmn_list$or_str_tmo),".",substr(tmn_list$or_str_tmo,4,8))
  aff_weak_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$aff_weak_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(aff_weak_orig)>0) names(aff_weak_orig) = paste0(names(tmn_list$aff_weak_tmo),".",substr(tmn_list$aff_weak_tmo,4,8))
  rp_weak_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$rp_weak_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(rp_weak_orig)>0) names(rp_weak_orig) = paste0(names(tmn_list$rp_weak_tmo),".",substr(tmn_list$rp_weak_tmo,4,8))
  and_weak_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$and_weak_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(and_weak_orig)>0) names(and_weak_orig) = paste0(names(tmn_list$and_weak_tmo),".",substr(tmn_list$and_weak_tmo,4,8))
  or_weak_orig = pentamerfreq_tcem[fmatch(substr(tmn_list$or_weak_tmo,4,8),names(pentamerfreq_tcem))]
  if(length(or_weak_orig)>0) names(or_weak_orig) = paste0(names(tmn_list$or_weak_tmo),".",substr(tmn_list$or_weak_tmo,4,8))
  aff_str_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$aff_str_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(aff_str_neo)>0) names(aff_str_neo) = paste0(names(tmn_list$aff_str_tmn),".",substr(tmn_list$aff_str_tmn,4,8))
  rp_str_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$rp_str_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(rp_str_neo)>0) names(rp_str_neo) = paste0(names(tmn_list$rp_str_tmn),".",substr(tmn_list$rp_str_tmn,4,8))
  and_str_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$and_str_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(and_str_neo)>0) names(and_str_neo) = paste0(names(tmn_list$and_str_tmn),".",substr(tmn_list$and_str_tmn,4,8))
  or_str_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$or_str_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(or_str_neo)>0) names(or_str_neo) = paste0(names(tmn_list$or_str_tmn),".",substr(tmn_list$or_str_tmn,4,8))
  aff_weak_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$aff_weak_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(aff_weak_neo)>0) names(aff_weak_neo) = paste0(names(tmn_list$aff_weak_tmn),".",substr(tmn_list$aff_weak_tmn,4,8))
  rp_weak_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$rp_weak_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(rp_weak_neo)>0) names(rp_weak_neo) = paste0(names(tmn_list$rp_weak_tmn),".",substr(tmn_list$rp_weak_tmn,4,8))
  and_weak_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$and_weak_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(and_weak_neo)>0) names(and_weak_neo) = paste0(names(tmn_list$and_weak_tmn),".",substr(tmn_list$and_weak_tmn,4,8))
  or_weak_neo = pentamerfreq_tcem[fmatch(substr(tmn_list$or_weak_tmn,4,8),names(pentamerfreq_tcem))]
  if(length(or_weak_neo)>0) names(or_weak_neo) = paste0(names(tmn_list$or_weak_tmn),".",substr(tmn_list$or_weak_tmn,4,8))
  
  #DIFFS
  aff_str_diff = aff_str_orig - aff_str_neo
  if(length(aff_str_diff)>0) names(aff_str_diff) = paste0(names(tmn_list$aff_str_tmn),".",substr(tmn_list$aff_str_tmo,4,8),".",substr(tmn_list$aff_str_tmn,4,8))
  rp_str_diff = rp_str_orig - rp_str_neo
  if(length(rp_str_diff)>0) names(rp_str_diff) = paste0(names(tmn_list$rp_str_tmn),".",substr(tmn_list$rp_str_tmo,4,8),".",substr(tmn_list$rp_str_tmn,4,8))
  and_str_diff = and_str_orig - and_str_neo
  if(length(and_str_diff)>0) names(and_str_diff) = paste0(names(tmn_list$and_str_tmn),".",substr(tmn_list$and_str_tmo,4,8),".",substr(tmn_list$and_str_tmn,4,8))
  or_str_diff = or_str_orig - or_str_neo
  if(length(or_str_diff)>0) names(or_str_diff) = paste0(names(tmn_list$or_str_tmn),".",substr(tmn_list$or_str_tmo,4,8),".",substr(tmn_list$or_str_tmn,4,8))
  aff_weak_diff = aff_weak_orig - aff_weak_neo
  if(length(aff_weak_diff)>0) names(aff_weak_diff) = paste0(names(tmn_list$aff_weak_tmn),".",substr(tmn_list$aff_weak_tmo,4,8),".",substr(tmn_list$aff_weak_tmn,4,8))
  rp_weak_diff = rp_weak_orig - rp_weak_neo
  if(length(rp_weak_diff)>0) names(rp_weak_diff) = paste0(names(tmn_list$rp_weak_tmn),".",substr(tmn_list$rp_weak_tmo,4,8),".",substr(tmn_list$rp_weak_tmn,4,8))
  and_weak_diff = and_weak_orig - and_weak_neo
  if(length(and_weak_diff)>0) names(and_weak_diff) = paste0(names(tmn_list$and_weak_tmn),".",substr(tmn_list$and_weak_tmo,4,8),".",substr(tmn_list$and_weak_tmn,4,8))
  or_weak_diff = or_weak_orig - or_weak_neo
  if(length(or_weak_diff)>0) names(or_weak_diff) = paste0(names(tmn_list$or_weak_tmn),".",substr(tmn_list$or_weak_tmo,4,8),".",substr(tmn_list$or_weak_tmn,4,8))

  
  tcemfreqs = list(
    aff_str_orig = aff_str_orig, aff_str_neo = aff_str_neo, aff_str_diff = aff_str_diff,
    rp_str_orig = rp_str_orig, rp_str_neo = rp_str_neo, rp_str_diff = rp_str_diff,
    and_str_orig = and_str_orig, and_str_neo = and_str_neo, and_str_diff = and_str_diff,
    or_str_orig = or_str_orig, or_str_neo = or_str_neo, or_str_diff = or_str_diff,
    aff_weak_orig = aff_weak_orig, aff_weak_neo = aff_weak_neo, aff_weak_diff = aff_weak_diff,
    rp_weak_orig = rp_weak_orig, rp_weak_neo = rp_weak_neo, rp_weak_diff = rp_weak_diff,
    and_weak_orig = and_weak_orig, and_weak_neo = and_weak_neo, and_weak_diff = and_weak_diff,
    or_weak_orig = or_weak_orig, or_weak_neo = or_weak_neo, or_weak_diff = or_weak_diff)
  save(tcemfreqs, file = paste0(ext_folder1,"01out/tcem_mutated_nonamers_tcemfreqs/", x))
})

#Drop patients without data
patdropped = ids[sapply(ids, function(x) {
  load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", x))
  all(lengths(tcemfreqs)==0)
})]

for(i in 1:length(patdropped)) {
  unlink(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", patdropped[i]))
} #8887

# load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", ids[1]))
# value_names = names(tcemfreqs)
# save(value_names, file = paste0(ext_folder1,"01out/value_names"))
```

##All mutations - median per individual

```{r}
ids = list.files(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs")) #8887
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1, "objects/tumortypes"))
load(paste0(ext_folder1, "01out/value_names"))

tumors_tcemfreqs = lapply(tumors, function(x) {
  tempids = names(tt)[tt == x]
  tempids = tempids[tempids %in% ids]
  temp_tcemfreqs = lapply(tempids, function(y) {
    load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", y))
    md = c(aff_str_orig = median(tcemfreqs$aff_str_orig, na.rm = T), 
           aff_str_neo = median(tcemfreqs$aff_str_neo, na.rm = T), 
           aff_str_diff = median(tcemfreqs$aff_str_diff, na.rm = T),
           rp_str_orig = median(tcemfreqs$rp_str_orig, na.rm = T), 
           rp_str_neo = median(tcemfreqs$rp_str_neo, na.rm = T), 
           rp_str_diff = median(tcemfreqs$rp_str_diff, na.rm = T),
           or_str_orig = median(tcemfreqs$or_str_orig, na.rm = T), 
           or_str_neo = median(tcemfreqs$or_str_neo, na.rm = T), 
           or_str_diff = median(tcemfreqs$or_str_diff, na.rm = T),
           and_str_orig = median(tcemfreqs$and_str_orig, na.rm = T), 
           and_str_neo = median(tcemfreqs$and_str_neo, na.rm = T), 
           and_str_diff = median(tcemfreqs$and_str_diff, na.rm = T),
           aff_weak_orig = median(tcemfreqs$aff_weak_orig, na.rm = T), 
           aff_weak_neo = median(tcemfreqs$aff_weak_neo, na.rm = T), 
           aff_weak_diff = median(tcemfreqs$aff_weak_diff, na.rm = T),
           rp_weak_orig = median(tcemfreqs$rp_weak_orig, na.rm = T), 
           rp_weak_neo = median(tcemfreqs$rp_weak_neo, na.rm = T),
           rp_weak_diff = median(tcemfreqs$rp_weak_diff, na.rm = T),
           or_weak_orig = median(tcemfreqs$or_weak_orig, na.rm = T), 
           or_weak_neo = median(tcemfreqs$or_weak_neo, na.rm = T), 
           or_weak_diff = median(tcemfreqs$or_weak_diff, na.rm = T),
           and_weak_orig = median(tcemfreqs$and_weak_orig, na.rm = T),
           and_weak_neo = median(tcemfreqs$and_weak_neo, na.rm = T),
           and_weak_diff = median(tcemfreqs$and_weak_diff, na.rm = T))
    names(md) = value_names
    md
  })
  names(temp_tcemfreqs) = tempids
  temp_tcemfreqs = do.call(rbind,temp_tcemfreqs)
})
names(tumors_tcemfreqs) = tumors
tumors_tcemfreqs$acc %>% View()
save(tumors_tcemfreqs, file = paste0(ext_folder1,"01out/tumors_tcemfreqs_all_mpi"))
```

##Passenger mutations - median per individual - 

```{r}
ids = list.files(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs")) #8887
load(paste0(ext_folder1, "objects/driver_mutations"))
load(paste0(ext_folder1, "objects/tumortypes"))
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1, "01out/value_names"))

tumors_tcemfreqs = lapply(tumors, function(x) {
  tempids = names(tt)[tt == x]
  tempids = tempids[tempids %in% ids]
  temp_tcemfreqs = lapply(tempids, function(y) {
    load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", y))
    tcemfreqs = lapply(tcemfreqs, function(z) {
      tempmuts = sapply(names(z), function(w) paste0(strsplit(w,"\\.")[[1]][1:3], collapse = "."))
      names(z) = tempmuts
      z = z[names(z) %nin% driver]
    })
    md = c(aff_str_orig = median(tcemfreqs$aff_str_orig, na.rm = T), 
           aff_str_neo = median(tcemfreqs$aff_str_neo, na.rm = T), 
           aff_str_diff = median(tcemfreqs$aff_str_diff, na.rm = T),
           rp_str_orig = median(tcemfreqs$rp_str_orig, na.rm = T), 
           rp_str_neo = median(tcemfreqs$rp_str_neo, na.rm = T), 
           rp_str_diff = median(tcemfreqs$rp_str_diff, na.rm = T),
           or_str_orig = median(tcemfreqs$or_str_orig, na.rm = T), 
           or_str_neo = median(tcemfreqs$or_str_neo, na.rm = T), 
           or_str_diff = median(tcemfreqs$or_str_diff, na.rm = T),
           and_str_orig = median(tcemfreqs$and_str_orig, na.rm = T), 
           and_str_neo = median(tcemfreqs$and_str_neo, na.rm = T), 
           and_str_diff = median(tcemfreqs$and_str_diff, na.rm = T),
           aff_weak_orig = median(tcemfreqs$aff_weak_orig, na.rm = T), 
           aff_weak_neo = median(tcemfreqs$aff_weak_neo, na.rm = T), 
           aff_weak_diff = median(tcemfreqs$aff_weak_diff, na.rm = T),
           rp_weak_orig = median(tcemfreqs$rp_weak_orig, na.rm = T), 
           rp_weak_neo = median(tcemfreqs$rp_weak_neo, na.rm = T),
           rp_weak_diff = median(tcemfreqs$rp_weak_diff, na.rm = T),
           or_weak_orig = median(tcemfreqs$or_weak_orig, na.rm = T), 
           or_weak_neo = median(tcemfreqs$or_weak_neo, na.rm = T), 
           or_weak_diff = median(tcemfreqs$or_weak_diff, na.rm = T),
           and_weak_orig = median(tcemfreqs$and_weak_orig, na.rm = T),
           and_weak_neo = median(tcemfreqs$and_weak_neo, na.rm = T),
           and_weak_diff = median(tcemfreqs$and_weak_diff, na.rm = T))
    names(md) = value_names
    md
  })
  names(temp_tcemfreqs) = tempids
  temp_tcemfreqs = do.call(rbind,temp_tcemfreqs)
})
names(tumors_tcemfreqs) = tumors
tumors_tcemfreqs$acc %>% View()
save(tumors_tcemfreqs, file = paste0(ext_folder1,"01out/tumors_tcemfreqs_pass_mpi"))
```

##All mutations - not aggragated per individual

```{r}
ids = list.files(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs")) #8887
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1, "objects/tumortypes"))

tumors_tcemfreqs = lapply(tumors, function(x) {
  tempids = names(tt)[tt == x]
  tempids = tempids[tempids %in% ids]
  temp_tcemfreqs = lapply(tempids, function(y) {
    load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", y))
    m = max(lengths(tcemfreqs), na.rm = T)
    sapply(tcemfreqs, function(p) fillnafun(p, m)) #create matrix
  })
  names(temp_tcemfreqs) = tempids
  temp_tcemfreqs = do.call(rbind,temp_tcemfreqs)
})
names(tumors_tcemfreqs) = tumors
save(tumors_tcemfreqs, file = paste0(ext_folder1,"01out/tumors_tcemfreqs_all_napi"))
```

##Passenger mutations - not aggragated per individual

```{r}
ids = list.files(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs")) #8887
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1, "objects/tumortypes"))
load(paste0(ext_folder1, "objects/driver_mutations"))
load(paste0(ext_folder1, "01out/value_names"))

tumors_tcemfreqs = lapply(tumors, function(x) {
  tempids = names(tt)[tt == x]
  tempids = tempids[tempids %in% ids]
  temp_tcemfreqs = lapply(tempids, function(y) {
    load(paste0(ext_folder1, "01out/tcem_mutated_nonamers_tcemfreqs/", y))
    tcemfreqs = lapply(tcemfreqs, function(z) {
      tempmuts = sapply(names(z), function(w) paste0(strsplit(w,"\\.")[[1]][1:3], collapse = "."))
      names(z) = tempmuts
      z = z[names(z) %nin% driver]
    })
    m = max(lengths(tcemfreqs), na.rm = T)
    if(m==0) {
      matrix(NA,nrow = 0, ncol = length(value_names), dimnames = list(NULL,value_names))
    } else {
      sapply(tcemfreqs, function(p) fillnafun(p, m)) #create matrix
    }
  })
  names(temp_tcemfreqs) = tempids
  temp_tcemfreqs = do.call(rbind,temp_tcemfreqs)
})
names(tumors_tcemfreqs) = tumors
tumors_tcemfreqs$acc %>% View()
save(tumors_tcemfreqs, file = paste0(ext_folder1,"01out/tumors_tcemfreqs_pass_napi"))
```

##Plots
###1 All

```{r}
load(paste0(ext_folder1, "01out/value_names"))
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1,"objects/study_abbrev"))

bplot = function(x) {
  sv = c(x,paste(strsplit(x,"_")[[1]][1],strsplit(x,"_")[[1]][2],"neo",sep = "_"))
  tempdf = res0 %>% select(study, sv)
  colnames(tempdf) = c("study", "orig", "neo")
  tempdf %<>% mutate(study = fct_reorder(.f = study, .x = neo, .fun = function(z) median(z, na.rm = T)))
  tempdf %<>% 
    tidyr::gather(key = origvsneo, value = mediantcemfreq, 2:3)
  tempdf$origvsneo = factor(tempdf$origvsneo, levels = c("orig","neo"))
  fig = ggplot(tempdf, aes(x = study, y = mediantcemfreq, fill = origvsneo)) + 
    geom_boxplot(outlier.shape = NA) + 
    scale_y_continuous(trans = "pseudo_log", breaks = seq(2,10,2)) +
    geom_hline(yintercept = seq(2,10,2), linetype = "dashed") +    
    theme_bw() +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size = 16, vjust = 0),
        axis.title.y = element_text(size = 16, vjust = 1),
        axis.text.x = element_text(vjust = 0.5, hjust = 1, angle = 90),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))
    return(fig)
}

bplot_diff = function(z) {
  tempdf = res0 %>% select(study, z)
  colnames(tempdf) = c("study", "diff")
  tempdf %<>% mutate(study = fct_reorder(.f = study, .x = diff, .fun = function(z) median(z, na.rm = T)))
  fig = ggplot(tempdf, aes(x = study, y = diff)) + 
    geom_boxplot(outlier.shape = NA) + 
    scale_y_continuous(trans = "pseudo_log", breaks = seq(1,5,1)) +
    geom_hline(yintercept = seq(1,5,1), linetype = "dashed") +    
    theme_bw() +
      theme(
        legend.position = "none",
        axis.title.x = element_text(size = 16, vjust = 0),
        axis.title.y = element_text(size = 16, vjust = 1),
        axis.text.x = element_text(vjust = 0.5, hjust = 1, angle = 90),
        axis.text.y = element_text(size = 8, color = "black"),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))
    return(fig)
}

tcemfreqs_files = grep("tumors_tcemfreqs", list.files(paste0(ext_folder1,"01out/")),value = T)

for(i in tcemfreqs_files) {
  id1 = paste0(strsplit(i,"_")[[1]][3:4], collapse = "_")
  load(paste0(ext_folder1,"01out/", i))
  res0 = matrix(ncol = (length(value_names)+1), dimnames = list(NA,c("tumor", value_names)))
  for(i in 1:length(tumors)) {
    res0 = rbind(res0, cbind.data.frame(tumor = tumors[i], tumors_tcemfreqs[[tumors[i]]]))
  }
  rm(i)
  res0 = res0[-1,]
  res0 = cbind(res0, study= study_abbrev[match(res0$tumor, study_abbrev$abb),"study"])
  #PLOT - orig vs neo
  for(j in grep("orig", value_names, value = T)) {
    id2 = paste(strsplit(j,"_")[[1]][1],strsplit(j,"_")[[1]][2],sep = "_")
    bplot(x = j)
    ggsave(filename = paste0(ext_folder1,"01out/plots/", id1, "_", id2, ".jpg"), width = 35, height = 25, units = "cm", dpi = "retina")
  }
  #PLOT - diff
  for(k in grep("diff", value_names, value = T)) {
    id3 = paste(strsplit(k,"_")[[1]][1],strsplit(k,"_")[[1]][2],sep = "_")
    bplot_diff(z = k)
    ggsave(filename = paste0(ext_folder1,"01out/plots/", id1, "_", id3, "_diff.jpg"), width = 35, height = 25, units = "cm", dpi = "retina")
  }
}

```

###2. Random sampling

```{r}
load(paste0(ext_folder1,"01out/tumors_tcemfreqs_all_napi")) #OR
load(paste0(ext_folder1,"01out/tumors_tcemfreqs_pass_napi"))

load(paste0(ext_folder1, "01out/value_names"))
load(paste0(ext_folder1, "objects/tumors"))
load(paste0(ext_folder1,"objects/study_abbrev"))

nonamer_count= sapply(tumors_tcemfreqs, function(x) {
  x %<>% as.data.frame()
  sapply(colnames(x), function(y) {
    x %>% pull(y) %>% na.omit() %>% length()
  })
}) #mennyi nonamer van egyes változokhoz tumoronkent

nonamer_mins = sapply(value_names, function(x) {min(nonamer_count[x,])}) #az egyes változókból mennyi a minimum nonamer szám

tcemfreqs_samples = lapply(grep("orig", value_names, value = T), function(k) {
  k_neo = paste(strsplit(k,"_")[[1]][1], strsplit(k,"_")[[1]][2], "neo", sep = "_")
  k_dif = paste(strsplit(k,"_")[[1]][1], strsplit(k,"_")[[1]][2], "diff", sep = "_")
  temp = lapply(tumors_tcemfreqs, function(z) {
    orig = z[,k]
    orig = orig[!is.na(orig)]
    neo = z[,k_neo]
    neo = neo[!is.na(neo)]
    dif = z[,k_dif]
    dif = dif[!is.na(dif)]
    indices = sample(1:length(orig),nonamer_mins[k])
    tempmtx = cbind(orig = orig[indices], neo = neo[indices], dif = dif[indices])
    colnames(tempmtx) = c(k, k_neo, k_dif)
    tempmtx
  })
  temp = do.call(cbind.data.frame, temp)
  colnames(temp) = sapply(colnames(temp), function(l) paste(strsplit(l,"\\.")[[1]][1],strsplit(l,"_")[[1]][3], sep = "_"))
  temp
})
names(tcemfreqs_samples) = gsub("_orig", "", grep("orig", value_names, value = T))
rm(nonamer_mins, nonamer_count)

for(i in names(tcemfreqs_samples)) {
  tempdf = tcemfreqs_samples[[i]]
  #ORIG vs NEO
  tempdf_on = tempdf[,colnames(tempdf)[!grepl("diff", colnames(tempdf))]]
  tempdf_on %<>% gather() %>% separate(col = 1, into = c("tumor", "pepsource"))
  tempdf_on = cbind(tempdf_on, study = study_abbrev[match(tempdf_on$tumor, study_abbrev$abb),"study"])
  tempdf_on2 = tempdf_on[tempdf_on$pepsource == "neo",]
  tempdf_on2$study = fct_reorder(.f = tempdf_on2$study, .x = tempdf_on2$value)
  tempdf_on$study = factor(tempdf_on$study, levels = levels(tempdf_on2$study))
  tempdf_on$pepsource = factor(tempdf_on$pepsource, levels = c("orig", "neo"))
  ggplot(tempdf_on, aes(x = study, y = value, fill = pepsource)) + 
    geom_boxplot() + geom_boxplot(outlier.shape = NA) + 
    scale_y_continuous(trans = "pseudo_log", breaks = seq(2,10,2)) +
    geom_hline(yintercept = seq(2,10,2), linetype = "dashed") +    
    theme_bw() +
    theme(
      legend.position = "bottom",
      axis.title.x = element_text(size = 16, vjust = 0),
      axis.title.y = element_text(size = 16, vjust = 1),
      axis.text.x = element_text(vjust = 0.5, hjust = 1, angle = 90),
      axis.text.y = element_text(size = 8, color = "black"),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"))
  ggsave(filename = paste0(ext_folder1,"01out/plots/random_pass_",i,".jpg"), width = 35,height = 25,units = "cm",dpi = "retina")
  #DIFF
  tempdf_dif = tempdf[,colnames(tempdf)[grepl("diff", colnames(tempdf))]]
  tempdf_dif %<>% gather() %>% separate(col = 1, into = "tumor")
  tempdf_dif = cbind(tempdf_dif, study = study_abbrev[match(tempdf_dif$tumor, study_abbrev$abb),"study"])
  tempdf_dif$study = fct_reorder(.f = tempdf_dif$study, .x = tempdf_dif$value)
  ggplot(tempdf_dif, aes(x = study, y = value)) + 
    geom_boxplot() + geom_boxplot(outlier.shape = NA) + 
    scale_y_continuous(trans = "pseudo_log", breaks = seq(1,5,1)) +
    geom_hline(yintercept = seq(1,5,1), linetype = "dashed") +    
    theme_bw() +
    theme(
      legend.position = "bottom",
      axis.title.x = element_text(size = 16, vjust = 0),
      axis.title.y = element_text(size = 16, vjust = 1),
      axis.text.x = element_text(vjust = 0.5, hjust = 1, angle = 90),
      axis.text.y = element_text(size = 8, color = "black"),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"))
  ggsave(filename = paste0(ext_folder1,"01out/plots/random_pass_diff_",i,".jpg"), width = 35,height = 25,units = "cm",dpi = "retina")
}
rm(tempdf,tempdf2,i)
```

#Ratio of neononamers with low TCEM frequency (<4)

```{r}
load(paste0(ext_folder1,"objects/study_abbrev"))
load(paste0(ext_folder1,"01out/tumors_tcemfreqs_pass_napi"))
vals = unique(gsub("_diff", "", gsub("_neo", "", gsub("_orig", "", colnames(tumors_tcemfreqs$acc)))))

neolowtcemfreq = sapply(tumors_tcemfreqs, function(x) {
  tempdf = as.data.frame(x)
  sapply(vals, function(y) {
    tempdf2 = na.omit(tempdf[,c(paste0(y, "_orig"), paste0(y, "_neo"))])
    colnames(tempdf2) = c("orig","neo")
    ratio = nrow(subset(tempdf2, orig >= 4 & neo < 4)) / nrow(tempdf2)
    names(ratio) = y
    ratio
  })
})

neolowtcemfreq = as.data.frame(neolowtcemfreq)
neolowtcemfreq$bt = vals #binding_type
neolowtcemfreq = gather(data = neolowtcemfreq, key = "tumor", value = "ratio", -bt)

for(i in vals) {
  tempdf = neolowtcemfreq[neolowtcemfreq$bt == i,]
  tempdf = cbind(tempdf, study = study_abbrev[match(tempdf$tumor, study_abbrev$abb),"study"])
  tempdf$study = fct_reorder(.f = tempdf$study, .x = tempdf$ratio)
  View(data.frame(levels(tempdf$study)))
  ggplot(tempdf, aes(study, ratio)) + geom_point() + theme(axis.text.x = element_text(angle = 90))
  ggsave(filename = paste0(ext_folder1,"01out/plots/neolowtcemfreq_",i,".jpg"), width = 25,height = 15,units = "cm",dpi = "retina")
}

```
